Pew_Cleaning

### 2021-03-31 pclean.Rmd
clean up

## Initial Data Import
```{r}
# Data set from Pew 
pew <- read_sav("../Pew/ATP W49.sav")

# Add the QKEY col
df <- pew$QKEY

# Iterate through data set
for(i in 2:(ncol(pew)-1)){ #skip the QKEY column (1st col) and the WEIGHT_W49 col (last col)
        temp <- as_factor(pew[ , i])
        df <- cbind(df,temp)
        temp <- 0
}

# Add the WEIGHT_W49 col
temp <- as_factor(pew[ , ncol(pew)])
df <- cbind(df,temp)

# Show df
head(df)

# Save the file 
if(!file.exists("../Pew/pewTech.RData") ) {
    write.csv(df, "../Pew/Pew_Tech.csv")
    save(df, file = "../Pew/pewTech.RData")
}

@@

```{r}
pew$haveSmartSpeak <-as_factor(pew$HOMEASSIST1_W49)
pew$tracked <-as_factor(pew$TRACKCO1a_W49)

df %>% drop_na(TRACKCO1a_W49) %>% ggplot(aes(x = TRACKCO1a_W49, fill = HOMEASSIST1_W49)) +
        geom_bar(position = "dodge", color = 'black') +
        theme(axis.text.x = element_text(angle=25, hjust = 1)) +
        labs( title = 'Dodged Bar Chart: \nDo Smart Speaker Owners Think They Are Being Tracked Online',
            x = "Opnion on How Much of What You Do Online is Being Tracked",
            y = "Count",
            fill = "Smart Speaker Ownership",
            caption = "Pew Research Data")
```

```{r}
df %>% drop_na(TRACKCO1a_W49) %>%  filter(HOMEASSIST1_W49 != "Refused") %>% ggplot(aes(x = TRACKCO1a_W49, fill = TRACKCO1a_W49)) +
        geom_bar(color = 'black') +
        facet_wrap(HOMEASSIST1_W49~., nrow = 2) +
        geom_text(stat='count', aes(label=..count..), vjust= -.5) +
        ylim(0,800) +
        theme(axis.text.x = element_text(angle=25, hjust = 1)) +
        labs( title = 'Faceted Bar Chart: \nDo Smart Speaker Owners Think They Are Being Tracked Online',
            x = "Opnion on How Much of What You Do Online is Being Tracked",
            y = "Count",
            fill = "Smart Speaker Ownership",
            caption = "Pew Research Data")

>>>>

## Initial Data Import
```{r}
# Data set from Pew 
importedData <- read_sav("../Pew/ATP W49.sav")

# Add the QKEY col
pew <- importedData$QKEY

# Iterate through data set
for(i in 2:(ncol(importedData)-1)){ #skip the QKEY column (1st col) and the WEIGHT_W49 col (last col)
        temp <- as_factor(importedData[ , i])
        pew <- cbind(pew,temp)
        temp <- 0
}

# Add the WEIGHT_W49 col
temp <- as_factor(importedData[ , ncol(importedData)])
pew <- cbind(pew,temp)

# Show pew
head(pew)

# Save the file 
if(!file.exists("../Pew/pewTech.RData") ) {
    write.csv(pew, "../Pew/Pew_Tech.csv")
    save(pew, file = "../Pew/pewTech.RData")
}

@@

```{r}
load("../Pew/pewTech.RData")

pew %>% drop_na(TRACKCO1a_W49) %>% ggplot(aes(x = TRACKCO1a_W49, fill = HOMEASSIST1_W49)) +
        geom_bar(position = "dodge", color = 'black') +
        theme(axis.text.x = element_text(angle=25, hjust = 1)) +
        labs( title = 'Dodged Bar Chart: \nDo Smart Speaker Owners Think They Are Being Tracked Online',
            x = "Opnion on How Much of What You Do Online is Being Tracked",
            y = "Count",
            fill = "Smart Speaker Ownership",
            caption = "Pew Research Data")
```

```{r}
pew %>% drop_na(TRACKCO1a_W49) %>%  filter(HOMEASSIST1_W49 != "Refused") %>% ggplot(aes(x = TRACKCO1a_W49, fill = TRACKCO1a_W49)) +
        geom_bar(color = 'black') +
        facet_wrap(HOMEASSIST1_W49~., nrow = 2) +
        geom_text(stat='count', aes(label=..count..), vjust= -.5) +
        ylim(0,800) +
        theme(axis.text.x = element_text(angle=25, hjust = 1)) +
        labs( title = 'Faceted Bar Chart: \nDo Smart Speaker Owners Think They Are Being Tracked Online',
            x = "Opnion on How Much of What You Do Online is Being Tracked",
            y = "Count",
            fill = "Smart Speaker Ownership",
            caption = "Pew Research Data")
